\section{Data notes}
\subsection{Putting density in perspective}
\paragraph{Spacial distribution} where are the densest CZ? See panel a of Figure \ref{fig:map}
\input{../2_analysis/output/figures/density_geography.tex}


\paragraph{Persistence:} panel b of figure \ref{fig:map} shows that density is highly persistent. The slope coefficient from the regression in the figure is 1.04.

\paragraph{Summary statistics} selected summary statistics for the 625 CZ in my sample are shown in table \ref{tab:summary_statistics}.


\begin{table}
\caption{Selected summary statics for CZ, 2020}
\label{tab:summary_statistics}
\input{../2_analysis/output/tables/density_gap_summary_stats.tex}
\end{table}

\paragraph{What are the densest CZ?}
Table \ref{tab:cz_examples} shows examples of CZ at different points of the density distribution. Whenever available, the table lists the main city in the CZ.
\input{../2_analysis/output/tables/CZ_example_table.tex}


\subsection{Residualization procedure}
Throughout this document I explore the relationship between average wages (gender wage gap) and CZ population density. I am also interested in how this relationship has changed over time.

To discard the possibility that the observed relationships arise because of simple changes in the population composition, I compute average wages net of individuals' characteristics.

\paragraph{Procedure}
\benu
	\item I regress log of the individuals' wages on individual characteristics separately by year, including a gender $\times$ CZ fixed effect. Models are estimated separately for each census year.
	\beqns
		w_{igrt}=X_{irt}\gamma_t+\lambda_{rt}^g
	\eeqns
	\item $\hat{\lambda}_{grt}$ is my estimate of CZ wages, net of individual characteristics.
	\item I compute the CZ-specific gender gap as:
	\beqns
		gap_{rt}=\hat{\lambda}_{rt}^m-\hat{\lambda}_{rt}^f
	\eeqns
\eenu

Throughout the document, the control variables $X_{irt}$ come into for different sets:
\bitem
	\item \textbf{Basic controls:} age dummies, race dummies, and foreign born dummy.
	\item \textbf{Human capital:} basic controls + 4-level education dummies.
	\item \textbf{Industry controls:} human capital controls + $\approx$ 150 industry fixed effects.
	\item \textbf{Full controls:} industry controls + occupation fixed effects.
\eitem